---
title: "PTBinteRface"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{template}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a wrapper package for INRAE's PTB model - this can be installed as pre-built binaries from our r-universe repo:

```{r eval=FALSE}
install.packages("PTBinteRface", repos = c('https://ku-awdc.r-universe.dev', 'https://cloud.r-project.org'))
```

Alternatively, it can be built from source via our drat repository:

```{r eval=FALSE}
install.packages("PTBinteRface", repos=c(CRAN="https://cran.rstudio.com/", "ku-awdc"="https://ku-awdc.github.io/drat/"))
```

After installation, the model can be run using:

```{r}
library("PTBinteRface")
results <- run_ptb_model()
```

Information on the parameters is given in the help file for ?run_ptb_model, and examples of the data frame inputs are given in the underlying PTBinraeR package.

The output from the model is a named list of data frames corresponding to the files output by the model:

```{r}
results
```

